### 2010-02-19 trunk/deliverables/D5_1_1/fast_d5_1_1.tex
change any reference from "form element" to "form"
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@576 d8b0c59b-6544-0410-94d9-83a5658a058e

\begin{itemize}
	\item Section~\ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section~\ref{sub:linked_data}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section~\ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed. Some of the most important features added in this iteration are:
	\begin{itemize}
		\item support for form elements, operators and back-end services (see Section ...),
		\item convenience operations for recommendation and checking satisfaction and reachability for form elements, operators and back-end services (see Section ...),
		\item and, last but not least, support for Screen planning (see Section~\ref{sub:planning}).
	\end{itemize}
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
	\item Appendix A. Last year an evaluation to choose the best technology for the Catalogue was done. It was not included in any formal deliverable, so this year it has been documented as an appendix.
\end{itemize}

>>>>

\begin{itemize}
	\item Section~\ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section~\ref{sub:linked_data}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section~\ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed. Some of the most important features added in this iteration are:
	\begin{itemize}
		\item support for forms, operators and back-end services (see Section ...),
		\item convenience operations for recommendation and checking satisfaction and reachability for forms, operators and back-end services (see Section ...),
		\item and, last but not least, support for Screen planning (see Section~\ref{sub:planning}).
	\end{itemize}
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
	\item Appendix A. Last year an evaluation to choose the best technology for the Catalogue was done. It was not included in any formal deliverable, so this year it has been documented as an appendix.
\end{itemize}
